Recent Advances in Smartphone Computational Photography

### 2020-11-15 paper.tex
Updates from Overleaf

@@

\author{
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
\alignauthor
Paul Friederichsen\\
	\affaddr{Division of Science and Mathematics}\\
	\affaddr{University of Minnesota, Morris}\\
	\affaddr{Morris, Minnesota, USA 56267}\\
	\email{fried701@morris.umn.edu}
}

@@

Smartphone cameras use very small sensors with fixed apertures. This means their ability to gather light is significantly reduced compared to larger dedicated cameras. Most modern smartphones use a burst system to capture multiple images when the user presses the capture button and merges them to improve image quality.

@@

\begin{figure}
\centering
%\psfig{file=figures/Bayer_pattern_on_sensor.pdf,width =3in}
\includegraphics[width=20pc]{Bayer_pattern_on_sensor}
\caption{A Bayer pattern on a sensor in isometric perspective.~\cite{wiki:BayerFilter}}
\label{fig:BayerPattern}
\end{figure}

\begin{figure*}[t]
\centering
% TODO: Size correctly for width
%\psfig{file=figures/Wronski2019-figure-2.pdf,width =7in}
\includegraphics[width=42pc]{Wronski2019-figure-2}
\caption{An overview of the approach used by Wronski et al.~\cite{Wronski2019}. The initial burst of input frames (a) are aligned (d) to a base frame. The local features in the frames (b) are used to create kernels (c) (Section~\ref{sec:kernelReconstruction}) which are used along with the motion robustness model (f) (Section~\ref{sec:robustnessModel}) to combine (g) the frames separately for each color channel. The final image (h) is produced by normalizing the results of each channel.}
\label{fig:Wronski2019Fig2}
\end{figure*}

@@

An image processing pipeline refers to the process the raw data from a camera sensor goes through to be turned into the final image file that can be displayed and shared.

Most smartphones use a burst processing pipeline for their cameras. Generally, burst processing involves taking a series of raw exposures and merging them together to form the final image. Most smartphones operate in a \emph{zero-shutter lag} mode by default. In this mode raw frames (the full unprocessed sensor output) are continuously captured to a temporary memory while the camera app is open. When the user presses the shutter button, several of the most recent frames are sent to the camera processing pipeline.

Both of the approaches in this paper build on the end-to-end burst processing pipeline from Hasinoff et al. \cite{Hasinoff2016} which used bursts of constant low-exposure frames to increase dynamic range and signal-to-noise ratio.

@@

\begin{figure*}
\centering
% TODO: Size correctly for width
\includegraphics[width=42pc]{Wronski2019-figure-4}
\caption{An illustration of subpixel displacements from a burst of four frames with linear hand motion. Each frame is offset by half a pixel on the x-axis and a quarter pixel on the y-axis from the last frame. After alignment, the pixel centers (black dots) uniformly cover the image with greater density than a single frame.~\cite{Wronski2019}}
\label{fig:Wronski2019Fig4}

@@

\subsection{Proposed super-resolution approach}

\begin{figure}
\centering
\includegraphics[width=18pc]{figures/Wronski2019-figure-8.pdf}
\caption{Plots of relative weights as a function of local features. The scale on the right indicates the weight given to each pixel in the $3\times 3$ neighborhood.~\cite{Wronski2019}}
\label{fig:Wronski2019Fig8}
% Merge kernels: Plots of relative weights in difgerent 3 × 3 sampling
% kernels as a function of local tensor features
\end{figure}

Super-resolution involves recreating a higher resolution signal from many lower resolution samples. Due to the random distribution of pixel shifts that result from hand movement, kernel regression was deemed a good technique for this reconstruction. Wronski et al. used anisotropic Gaussian Radial Basis Function (RBF) kernels (Section~\ref{sec:kernelReconstruction}) and a statistical robustness model (Section~\ref{sec:robustnessModel}) to combine burst frames into a higher resolution image.

\subsubsection{Kernel reconstruction}
\label{sec:kernelReconstruction}

The core idea of the algorithm is considering the pixels of multiple raw frames as randomly offset, aliased, and noisy measurements of three original continuous signals, one for each color channel. The algorithm creates the final output image pixel-by-pixel. For each output pixel, it evaluates the local contributions to each of the three color channels from different input frames since each raw image pixel is specific to a single color channel.

@@

\subsubsection{Motion Robustness}
\label{sec:robustnessModel}

\begin{figure}
\centering
\includegraphics[width=20pc]{figures/wronski2019-figure-9-95quality.jpg}
\caption{A photograph of a moving bus: \textbf{Left}: Without a motion robustness model there are alignment errors and occlusions that result in tiling and ghosting artifacts. \textbf{Middle}: The robustness mask produced by the robustness model. White regions are those with all frames contributing to the final merged image and darker regions are those with a lower number of contributing frames. \textbf{Right}: The result of using the robustness model when merging frames. \cite{Wronski2019}}
\label{fig:Wronski2019Fig9}
\end{figure}

@@

\begin{figure}[]
\centering
\includegraphics[width=20pc]{figures/wronski2019-figure-1-100quality-crop.jpg}

\caption{A comparison of the traditional frame merging approach (\textbf{top}) and the approach by Wronski et al. (\textbf{bottom}). The super resolution merge algorithm improves sharpness and detail while eliminating the 
Moiré aliasing artifacts seen in the third (red) inset.~\cite{Wronski2019}}

@@

\subsection{Motion Metering}
\label{sec:motionMetering}

\begin{figure}
\centering
\includegraphics[width=20pc]{figures/liba2019-figure-7.pdf}
\caption{A traditional static exposure schedule compared to the dynamic exposure scheudle of Liba et al. at various levels of motion.~\cite{Liba2019}}
\label{fig:exposure}

@@

@@

\subsubsection{Stability detection}

More experienced photographers often brace their device against a surface or put it on a tripod in low-light situations. If this can be detected, longer exposures can be used without risk of motion blur. Liba et al.'s motion metering system captures up to 333 ms exposures when handheld but when stabilized it captures up to 1 second exposures. To detect a stabilized device, measurements from the device's gyroscope are averaged over a short time, 1.466 s, before the shutter button was pressed while masking out the last 0.4 s of the measurements to prevent vibrations from the user pressing the shutter button from affecting the result.

@@

%For burst merging, Liba et al. built upon the Fourier domain temporal merging from Hasinoff et al. \cite{Hasinoff2016}. This is used on some devices while those with a fast enough system-on-chip use the merging method from Wronski et al. (Section~\ref{sec:handheldSuperRes}).

@@

\subsection{Auto white balance in low-light}
\label{sec:autoWhiteBal}

\begin{figure}
\centering
\begin{subfigure}{9pc}
\centering
\includegraphics[width=9pc]{figures/0GMA_20180814_233948_174_qc.jpg}
\caption{Pixel default AWB}
\label{fig:whitebalance:default}
\end{subfigure}
\begin{subfigure}{9pc}
\centering
\includegraphics[width=9pc]{figures/0GMA_20180814_233948_174_gcam.jpg}
\caption{Liba et al.}
\label{fig:whitebalance:liba}
\end{subfigure}

@@

\begin{figure}
\centering
\includegraphics[width=20pc]{figures/Wright_of_Derby_The_Orrery}
\caption{ \emph{Philosopher Lecturing on the Orrery}, by Joseph Wright of Derby, 1766 \cite{file:theOrrery}. The artist depicts a dark scene with bright, colorful detail while still maintaining the nighttime aesthetic by increasing contrast, surrounding the scene with darkness, and making the shadow areas completely black.~\cite{blog:Wronski2018}}
\label{fig:theOrrery}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{6pc}
\centering
\includegraphics[width=6pc]{figures/liba2019-figure-14a-95quality.jpg}
\caption{Baseline}
\label{fig:toneMapping:baseline}
\end{subfigure}
\begin{subfigure}{6pc}
\centering
\includegraphics[width=6pc]{figures/liba2019-figure-14b-95quality.jpg}
\caption{CLAHE}
\label{fig:toneMapping:clahe}
\end{subfigure}
\begin{subfigure}{6pc}
\centering
\includegraphics[width=6pc]{figures/liba2019-figure-14c-95quality.jpg}
\caption{Liba et al.}
\label{fig:toneMapping:liba}
\end{subfigure}

\caption{An example of tone mapping a nighttime scene. (a) The tone mapping of Hasinoff et al. \cite{Hasinoff2016} produces too dark of an image whereas using a different tone mapping technique (b) that brightens using histogram equalization (CLAHE~\cite{CLAHE})results in more detail but lacking global contrast. The tone mapping from Liba et al. (c) retains detail but still has the global contrast and dark areas to look like a night scene.~\cite{Liba2019}}

@@

\begin{figure*}
\centering
\begin{subfigure}{13pc}
\centering
\includegraphics[width=13pc]{figures/liba2019-figure-1a-95quality.jpg}
\caption{Hasinoff et al.}
\label{fig:libaResults:hasinoff}
\end{subfigure}
\begin{subfigure}{13pc}
\centering
\includegraphics[width=13pc]{figures/liba2019-figure-1b-95quality.jpg}
\caption{Hasinoff et al. brightened}
\label{fig:libaResults:Hasinoff}
\end{subfigure}
\begin{subfigure}{13pc}
\centering
\includegraphics[width=13pc]{figures/liba2019-figure-1c-95quality.jpg}
\caption{Liba et al.}
\label{fig:libaResults:liba}
\end{subfigure}

@@

Additionally, Liba et al. developed a new error metric for training the model that better deals with heavily tinted illuminants which are common in night scenes (like those from colorful neon lights). The issue with traditional error metrics in low light is that they are based on how well the algorithm recovers \emph{all} of the color channels of the illuminant. This works well for the close to white true illumination of brighter scenes but in dark scenes with heavily tinted illuminants the white balanced image may contain pixel values where a single color channel's values are near zero for the whole image. Such an image would look the same under all possible transformations of that channel. When a color channel is ``missing" like this it can produce inaccurately low accuracy results from the error metric. It is also unclear how to set the missing channels in the ground-truth illuminant data.~\cite{Liba2019}

@@

Their TMO uses various heuristics on top of the tone mapping of Hasinoff et al. \cite{Hasinoff2016}. These include allowing higher overall gains, limiting the boosting of shadows, allowing compression of higher dynamic ranges, boosting the color saturation inversely to scene brightness, and adding a brightness-dependent vignette.~\cite{Liba2019}

@@

This system was launched in November 2018 on Pixel phones as the "Night Sight" mode in the camera app. On Pixel, Pixel 2, and Pixel 3a it uses a burst merging technique adapted from Hasiniff et al. \cite{Hasinoff2016} to better handle motion while on faster Pixel phones it uses the super-resolution merging algorithm described by Wronski et al. \cite{Wronski2019} (Section~\ref{sec:handheldSuperRes}). The comparisons and results here all use the former merging technique. \cite{Liba2019}

Liba et al. compared their system to the pipeline it built upon from Hasiniff et al. \cite{Hasinoff2016}. An example of their system producing lower noise, more detail, and more pleasing colors is shown in Figure~\ref{fig:libaResults}. They also compared their pipeline with neural network that operates on single raw images by Chen et al.~\cite{Chen2018} using frames from a similar camera to the one the neural network was trained on rather than a smartphone camera and still the system by Liba et al. produced higher-quality images. Additionally, Liba et al.'s system processes images much faster and with much less memory than the neural network by Chen et al. \cite{Chen2018}.~\cite{Liba2019}

More recently, Night Sight has added an astrophotography mode allowing for even longer exposures (as long as 1-4 minutes) which allows for sharp and clear images of stars and extremely dark landscapes~\cite{blog:Kainz2019}.

@@

New software techniques like these have allowed Google to continue using the same camera sensor hardware over multiple generations of their Pixel phones while continuing to be highly rated in photo quality. It has also enabled updates that continually improve the camera performance of previous Pixel phones to the point where they compete with the latest from other manufacturers. Computational photography will continue to become an ever more important part of cameras, both in smartphones and in other applications.

>>>>

\usepackage[
bookmarksnumbered,
hidelinks,
pdflang={en},
pdfdisplaydoctitle,
pdfauthor={Paul Friederichsen},
pdftitle={Recent Advances in Smartphone Computational Photography},
pdfkeywords={computational photography, super-resolution, image processing, low-light imaging}
]{hyperref}

%\urlstyle{rm}

\boilerplate={This work is licensed under the Creative Commons 
Attribution-NonCommercial-ShareAlike 4.0 International License. 
To view a copy of this license, visit 
\href{https://creativecommons.org/licenses/by-nc-sa/4.0/}{creativecommons.org/licenses/by-nc-sa/4.0/}.}

@@

\author{
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
\alignauthor
Paul Friederichsen\\
	\affaddr{Division of Science and Mathematics}\\
	\affaddr{University of Minnesota, Morris}\\
	\affaddr{Morris, Minnesota, USA 56267}\\
	\email{\href{mailto:fried701@morris.umn.edu}{fried701@morris.umn.edu}
	}
}

@@

Smartphone cameras use very small sensors with fixed apertures. This means their ability to gather light is significantly reduced compared to larger dedicated cameras. Most modern smartphones use a burst system to capture multiple images and merge them together to improve image quality.

@@

\begin{figure}
\centering
%\psfig{file=figures/Bayer_pattern_on_sensor.pdf,width =3in}
\includegraphics[width=\columnwidth]{Bayer_pattern_on_sensor}
\caption{A Bayer pattern on a sensor in isometric perspective.~\cite{wiki:BayerFilter}}
\label{fig:BayerPattern}
\end{figure}

\begin{figure*}[t]
\centering
% TODO: Size correctly for width
%\psfig{file=figures/Wronski2019-figure-2.pdf,width =7in}
\includegraphics[width=\textwidth]{Wronski2019-figure-2}
\caption{An overview of the approach used by Wronski et al.~\cite{Wronski2019}. The initial burst of input frames (a) are aligned (d) to a base frame. The local features in the frames (b) are used to create kernels (c) (Section~\ref{sec:kernelReconstruction}) which are used along with the motion robustness model (f) (Section~\ref{sec:robustnessModel}) to combine (g) the frames separately for each color channel. The final image (h) is produced by normalizing the results of each channel.}
\label{fig:Wronski2019Fig2}
\end{figure*}

@@

An image processing pipeline refers to the process the raw data from a camera sensor goes through to be turned into the final image file that can be displayed and shared. 
Most smartphones use a burst processing pipeline for their cameras. Generally, burst processing involves taking a series of exposures and merging them together to form the final image. Most smartphones operate in a \emph{zero-shutter lag} mode by default. In this mode, raw frames (the full unprocessed sensor output) are continuously captured to a temporary area in memory while the camera app is open. When the user presses the shutter button, several of the most recent frames are sent to the camera processing pipeline to be merged.

Both of the approaches in this paper build on the end-to-end burst processing pipeline from Hasinoff et al. \cite{Hasinoff2016} which used bursts of constant low-exposure frames to increase dynamic range and signal-to-noise ratio. It specifically uses under-exposed frames to reduce motion blur.

@@

\begin{figure*}
\centering
% TODO: Size correctly for width
\includegraphics[width=\textwidth]{Wronski2019-figure-4}
\caption{An illustration of subpixel displacements from a burst of four frames with linear hand motion. Each frame is offset by half a pixel on the x-axis and a quarter pixel on the y-axis from the last frame. After alignment, the pixel centers (black dots) uniformly cover the image with greater density than a single frame.~\cite{Wronski2019}}
\label{fig:Wronski2019Fig4}

@@

%\subsection{Proposed super-resolution approach}

%Super-resolution involves recreating a higher resolution signal from many lower resolution samples. Due to the random distribution of pixel shifts that result from hand movement, kernel regression was deemed a good technique for this reconstruction. Wronski et al. used anisotropic Gaussian Radial Basis Function (RBF) kernels (Section~\ref{sec:kernelReconstruction}) and a statistical robustness model (Section~\ref{sec:robustnessModel}) to combine burst frames into a higher resolution image.

\subsection{Kernel reconstruction}
\label{sec:kernelReconstruction}

\begin{figure}
\centering
\includegraphics[width=19pc]{figures/Wronski2019-figure-8.pdf}
\caption{Plots of relative weights as a function of local features. The scale on the right indicates the weight given to each pixel in the $3\times 3$ neighborhood.~\cite{Wronski2019}}
\label{fig:Wronski2019Fig8}
% Merge kernels: Plots of relative weights in difgerent 3 × 3 sampling
% kernels as a function of local tensor features
\end{figure}

The core idea of the algorithm is considering the pixels of multiple raw frames with hand motion as randomly offset, aliased, and noisy measurements of three original continuous signals, one for each color channel. The algorithm creates the final output image pixel-by-pixel. For each output pixel, it evaluates the local contributions to each of the three color channels from different input frames since each raw image pixel is specific to a single color channel.

@@

\subsection{Motion robustness}
\label{sec:robustnessModel}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/wronski2019-figure-9-95quality.jpg}
\caption{A photograph of a moving bus: \textbf{Left}: Without a motion robustness model there are alignment errors and occlusions that result in tiling and ghosting artifacts. \textbf{Middle}: The robustness mask produced by the robustness model. White regions are those with all frames contributing to the final merged image and darker regions are those with a lower number of contributing frames. \textbf{Right}: The result of using the robustness model when merging frames. \cite{Wronski2019}}
\label{fig:Wronski2019Fig9}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/wronski2019-figure-1-100quality-crop.jpg}

\caption{A comparison of the traditional frame merging approach (\textbf{top}) and the approach by Wronski et al. (\textbf{bottom}). The super resolution merge algorithm improves sharpness and detail while eliminating the 
Moiré aliasing artifacts seen in the third (\textbf{red}) frame.~\cite{Wronski2019}}

@@

\subsection{Motion metering}
\label{sec:motionMetering}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/liba2019-figure-7.pdf}
\caption{A traditional static exposure schedule compared to the dynamic exposure schedule of Liba et al. at various levels of motion.~\cite{Liba2019}}
\label{fig:exposure}

@@

Additionally, experienced photographers often brace their device against a surface or put it on a tripod in low light. Liba et al.'s motion metering system is able to use even longer exposures (up to 1 second) by detecting this using measurements from the device's gyroscope.

@@

%\subsubsection{Stability detection}

%More experienced photographers often brace their device against a surface or put it on a tripod in low-light situations. If this can be detected, longer exposures can be used without risk of motion blur. Liba et al.'s motion metering system captures up to 333 ms exposures when handheld but when stabilized it captures up to 1 second exposures. To detect a stabilized device, measurements from the device's gyroscope are averaged over a short time, 1.466 s, before the shutter button was pressed while masking out the last 0.4 s of the measurements to prevent vibrations from the user pressing the shutter button from affecting the result.

@@

%For burst merging, Liba et al. built upon the Fourier domain temporal merging from Hasinoff et al. \cite{Hasinoff2016}. This is used on some devices while those with a fast enough system-on-chip use the merging method from Wronski et al. (Section~\ref{setc:handheldSuperRes}).

@@

\subsection{Auto white balance in low light}
\label{sec:autoWhiteBal}

\begin{figure}
\centering
\begin{subfigure}{9.8pc}
\centering
\includegraphics[width=9.8pc]{figures/0GMA_20180814_233948_174_qc.jpg}
\caption{Pixel default AWB}
\label{fig:whitebalance:default}
\end{subfigure}
\begin{subfigure}{9.8pc}
\centering
\includegraphics[width=9.8pc]{figures/0GMA_20180814_233948_174_gcam.jpg}
\caption{Liba et al.}
\label{fig:whitebalance:liba}
\end{subfigure}

@@

@@

Additionally, Liba et al. developed a new error metric for training the model that better deals with heavily tinted illuminants which are common in night scenes (like those from colorful neon lights). The issue with traditional error metrics in low light is that they are based on how well the algorithm recovers \emph{all} of the color channels of the illuminant. This works well for the close to white true illumination of brighter scenes but in dark scenes with heavily tinted illuminants the white balanced image may contain pixel values where a single color channel's values are near zero for the whole image. Such an image would look the same under all possible transformations of that channel. 
\pagebreak 
When a color channel is ``missing" like this it can produce inaccurately low accuracy results from the error metric. It is also unclear how to set the missing channels in the ground-truth illuminant data.~\cite{Liba2019}

\begin{figure}
\centering
\includegraphics[trim={0 000 0 0}, clip=true, width=\columnwidth]{figures/Wright_of_Derby_The_Orrery}
\caption{ \emph{Philosopher Lecturing on the Orrery}, by Joseph Wright of Derby, 1766 \cite{file:theOrrery}. The artist depicts a dark scene with bright, colorful detail while still maintaining the nighttime aesthetic by increasing contrast, surrounding the scene in darkness, and keeping the shadow areas completely black.~\cite{blog:Wronski2018}}
\label{fig:theOrrery}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}{6.5pc}
\centering
\includegraphics[width=6.5pc]{figures/liba2019-figure-14a-95quality.jpg}
\caption{Baseline}
\label{fig:toneMapping:baseline}
\end{subfigure}
\begin{subfigure}{6.5pc}
\centering
\includegraphics[width=6.5pc]{figures/liba2019-figure-14b-95quality.jpg}
\caption{CLAHE}
\label{fig:toneMapping:clahe}
\end{subfigure}
\begin{subfigure}{6.5pc}
\centering
\includegraphics[width=6.5pc]{figures/liba2019-figure-14c-95quality.jpg}
\caption{Liba et al.}
\label{fig:toneMapping:liba}
\end{subfigure}

\caption{An example of tone mapping a night scene. The tone mapping of Hasinoff et al. \cite{Hasinoff2016} (\textbf{a}) produces too dark of an image while using a different tone mapping technique (\textbf{b}) that brightens using histogram equalization (CLAHE~\cite{CLAHE}) results in more detail but lacking global contrast. The tone mapping from Liba et al. (\textbf{c}) retains detail while keeping global contrast and dark areas to look like a night scene.~\cite{Liba2019}}

@@

\begin{figure*}
\centering
\begin{subfigure}{13.8pc}
\centering
\includegraphics[width=13.8pc]{figures/liba2019-figure-1a-95quality.jpg}
\caption{Hasinoff et al.}
\label{fig:libaResults:hasinoff}
\end{subfigure}
\begin{subfigure}{13.8pc}
\centering
\includegraphics[width=13.8pc]{figures/liba2019-figure-1b-95quality.jpg}
\caption{Hasinoff et al. brightened}
\label{fig:libaResults:Hasinoff}
\end{subfigure}
\begin{subfigure}{13.8pc}
\centering
\includegraphics[width=13.8pc]{figures/liba2019-figure-1c-95quality.jpg}
\caption{Liba et al.}
\label{fig:libaResults:liba}
\end{subfigure}

@@

@@

Their TMO uses various heuristics on top of the tone mapping of Hasinoff et al. \cite{Hasinoff2016}. These include allowing higher overall gains, limiting the boosting of shadows, allowing compression of higher dynamic ranges, boosting the color saturation inversely to scene brightness, and adding a brightness-dependent vignette.
It produces a more detailed image while maintaining global contrast and the nighttime aesthetic (Figure~\ref{fig:toneMapping:liba}).~\cite{Liba2019}

@@

This system was launched in November 2018 on Pixel phones as the ``Night Sight" mode in the camera app. On Pixel, Pixel 2, and Pixel 3a it uses a burst merging technique adapted from Hasiniff et al. \cite{Hasinoff2016} to better handle motion while on faster Pixel phones it uses the super-resolution merging algorithm described by Wronski et al. \cite{Wronski2019} (Section~\ref{sec:handheldSuperRes}). The comparisons and results here all use the former merging technique. \cite{Liba2019}

Liba et al. compared their system to the pipeline it built upon from Hasiniff et al. \cite{Hasinoff2016}. An example of their system producing lower noise, more detail, and more pleasing colors is shown in Figure~\ref{fig:libaResults}. They also compared their pipeline with neural network that operates on single raw images by Chen et al.~\cite{Chen2018} using frames from a similar camera to the one the neural network was trained on rather than a smartphone camera and still the system by Liba et al. produced higher-quality images and processed images much faster and using less memory.~\cite{Liba2019}

More recently, an astrophotography mode has been added to Night Sight allowing for even longer exposures (as long as 1-4 minutes) which allows for sharp and clear images of stars and extremely dark landscapes~\cite{blog:Kainz2019}.

@@

These new computational photography techniques and others like them have allowed Google to continue using the same camera sensor hardware over multiple generations of their Pixel phones while continuing to be highly rated in photo quality. It has also enabled updates that continually improve the camera performance of previous Pixel phones to the point where they compete with the latest from other manufacturers. 
Computational photography techniques will continue to be an ever more important part off cameras and image processing in smartphones, professional photography, and other applications.
